Towards Transparency and Open Science

### 2023-02-06 manuscript.Rmd
must -> has to
passive

Therefore, to provide transparency, computational reproducibility must satisfy two requirements.
First, computational reproducibility must ensure that the same data lead to the same results.
Second, computational reproducibility must make the inductive process repeatable on similar data.

@@

Computational reproducibility enables transparency about formal inductive processes.
However, informal inductive processes deprive us of complete transparency.
Therefore, it is prudent to replace informal induction with formal induction as much as possible.
If a researcher makes every effort only to employ formal inductive reasoning in a reproducible manner, they still must persuade their readers that they have not engaged in informal induction.

>>>>

Therefore, to provide transparency, computational reproducibility has to satisfy two requirements.
First, computational reproducibility must ensure that the same data lead to the same results.
Second, computational reproducibility must make the inductive process repeatable on similar data.

@@

Computational reproducibility enables transparency about formal inductive processes.
However, informal inductive processes deprive of complete transparency.
Therefore, it is prudent to replace informal induction with formal induction as much as possible.
If a researcher makes every effort only to employ formal inductive reasoning in a reproducible manner, they still must persuade their readers that they have not engaged in informal induction.
